{\bf {\Large Title....}}

### 2016-07-29 ident_manu.Rnw
sens_ests_all and sens_ests_cat_all to data
comparing parameter sensitivity between state variables, fix to par_txt

>>>>

% back of envelop calcs for number of relevant parms, all state variables
<<echo = F>>=

data(sens_ests_cat_all)

tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))

lims <- with(tmp, quantile(error, c(0.05, 0.95))) %>% 
  as.numeric

stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')

toplo <- filter(tmp, error < lims[2] & error > lims[1]) %>% 
  mutate(
    L1 = factor(L1, levels = stts_lev, labels = stts_lab)
  )
toplo1 <- filter(toplo, !Category %in% c('Phytoplankton', 'Zooplankton')) %>% 
  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
toplo2 <- filter(toplo, Category %in% c('Phytoplankton')) %>% 
  mutate(
    grp = gsub('^.*_([1-6])$', 'p\\1', Parameter), 
    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
  )
toplo3 <- filter(toplo, Category %in% c('Zooplankton')) %>% 
  mutate(
    grp = gsub('^.*_([1-2])$', 'z\\1', Parameter), 
    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
  )

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 8), 
  axis.text.y = element_text(size =8),
  axis.title.y = element_blank(), 
  axis.title.x = element_blank(),
  legend.position = 'none'
  )

p1 <- ggplot(toplo1, aes(x = Parameter, y = L1, fill = error)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0),
    breaks = toplo1$Parameter, 
    labels = parse(text = toplo1$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~Category, scales = 'free')
p2 <- ggplot(toplo2, aes(x = Parameter, y = L1, fill = error)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0), 
    breaks = toplo2$Parameter, 
    labels = parse(text = toplo2$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~grp, scales = 'free') + 
  ggtitle('Phytoplankton')
p3 <- ggplot(toplo3, aes(x = Parameter, y = L1, fill = error)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0), 
    breaks = toplo3$Parameter, 
    labels = parse(text = toplo3$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) + 
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~grp, scales = 'free') + 
  ggtitle('Zooplankton') + 
  theme(legend.position = 'right')
pleg <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')

grid.arrange(
  arrangeGrob(p1, p2, p3, ncol = 1), 
  pleg, ncol = 2, widths =  c(1, 0.1), 
  bottom = 'Parameter', 
  left = 'State variable'
)
@
